Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models

### 2023-04-20 Paper/draft.tex

Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation.

@@

In the rest of this section, differences of the $k_T$-factorization and the dipole-factorization are outlined.  In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed. In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at Electron-Ion Collider (EIC) and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\

Let us consider the inclusive DIS process $e p\rightarrow \gamma^* (q) p(p)\rightarrow X$. %where a proton and a photon interact, and their momenta are $p$ and $q$ respectively.
Additionally, let us introduce $q'\equiv q+x p$. 
Then one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.

If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\

>>>>

Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation. The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.

@@

In the rest of this section, differences of the $k_T$-factorization and the dipole-factorization are outlined.  In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed. In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\

Let us consider the inclusive DIS process $e p\rightarrow \gamma^* (q) p(p)\rightarrow X$. %where a proton and a photon interact, and their momenta are $p$ and $q$ respectively.
Additionally, let us introduce $q'\equiv q+x p$. 
Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
	\label{eq:angle-integrated}
\end{multline}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
	\label{eq:z}
\end{equation}
(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
%and
%\begin{equation}
%	\begin{split}
%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
%	\end{split}
%\end{equation}
%for
%\begin{equation}
%	\begin{split}
%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
%	\end{split}
%\end{equation}
%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\
